---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Set Up
## Required Packages
```{r, eval = FALSE}
library(dplyr)         # mutate_at
library(Matrix)
library("vegan")
library(tidyverse)
library(compositions)  # clr-transform
```

## Parameter
```{r, eval = FALSE}
THRESHOLD_abundancesum <- 100   # ASVs abundance sum over all stations has to be above 100
THRESHOLD_presence <- 0.05      # ASVs have to be present in more than 5% of the stations -> 397 stations --> 19.85 -> 20 stations
pseudo_count <- 1               # pseudocount that is added before clr transformation
PATH <- "/GlobalNetworkMalaspinaHotmix/"
```

## Read in files
```{r, eval = FALSE}
# Read in ASV files
path <- paste(PATH,"00_Tables/",sep="")
filename <- "Euk.txt"
Euk <- read.csv(paste(path,filename,sep=""), sep = "\t", header = TRUE)
filename <- "Prok.txt"
Prok <- read.csv(paste(path,filename,sep=""), sep = "\t", header = TRUE)

# Set rownames
rownames(Euk) <- Euk$ID
Euk$ID <- NULL
rownames(Prok) <- Prok$ID
Prok$ID <- NULL

# ENV
filename <- "ENV.txt"
ENV <- read.csv(paste(path,filename,sep=""), sep = "\t", dec = ".", header = TRUE)
```

## Check stations
Eukaryotic table and Prokaryotic table do not have the same stations! Thus, we have to find the stations that are present in both.
```{r, eval = FALSE}
E_stations <- colnames(Euk)
P_stations <- colnames(Prok)
I_stations <- intersect(E_stations, P_stations)
setdiff(E_stations, P_stations)
setdiff(P_stations, E_stations)
Euk_intersection <- Euk[,sort(I_stations)]
Prok_intersection <- Prok[,sort(I_stations)]
```
- Euk and Prok have 397 stations in common
-> 11 stations in Euk but not in Prok:
"MalaSurf_MD2695_3m" "MalaSurf_MD2926_3m" "MalaDeep_ST17_3943m" "MalaDeep_ST20_3942m" "MalaDeep_ST43_4000m" "MalaDeep_ST50_4000m" "MalaDeep_ST53_3500m" "MalaDeep_ST62_2400m" "MalaDeep_ST65_4000m" "MalaDeep_ST81_3500m" "MalaDeep_ST91_4000m"
-> 23 stations in Prok, but not in Euk:
"MalaVP_DNA_D2217_2800m" "MalaVP_DNA_D2799_1000m" "MalaVP_DNA_D2801_900m"  "MalaVP_DNA_D2805_150m"  "MalaVP_DNA_D2807_3m"    "MalaVP_DNA_D68_4000m"   "MalaVP_DNA_D72_1250m"  "MalaVP_DNA_D74_970m"
"MalaDeep_ST144_4000m"   "MalaDeep_ST32_3200m"    "MalaDeep_ST35_3650m"    "MalaDeep_ST67_4000m"    "MalaDeep_ST74_4000m"    "MalaDeep_ST82_2150m" 
"Hotmix_HM001_2230m"     "Hotmix_HM009_1500m"     "Hotmix_HM016_50m"       "Hotmix_HM017_3m"        "Hotmix_HM026_2752m"     "Hotmix_HM032_500m"      "Hotmix_HM041_200m"     "Hotmix_HM082_500m"      "Hotmix_HM099_50m"

Now the stations of the two tables are in the same order!
```{r, eval = FALSE}
sum(1*(colnames(Euk_intersection)==colnames(Prok_intersection)))==dim(Euk_intersection)[2]
```

# ENV table
## Reduce table to match intersection of Euk and Prok table
```{r, eval = FALSE}
rownames(ENV) <- ENV$ID
ENV_intersection <- ENV[colnames(Euk_intersection),]
```

## Missing Values
```{r}
t1 <- colSums(1*(is.na(ENV_intersection)))
t1 <- t1[which(t1>0)]
sort(t1)
sort(t1)/dim(ENV_intersection)[1]*100
```
There are numerous stations with at least one missing value:
ENV: number of missing values
Temperature                   2  (0.5037783%)
Salinity                      2  (0.5037783%)
Fluorescence                  3  (0.7556675%)
NO3_cruise_and_WOA13         36  (9.0680101%)
SiO4cruise_and_SiO4_WOA13    37  (9.3198992%)
PO4_cruise_and_PO4_WOA13     38  (9.5717884%)
Chlorophyll                  82 (20.6549118%)
NO2                         288 (72.5440806%)
- While most stations contain environmental information for Temperature, Salinity, and Flourescence (below 1% of missing values)
- below 10% no NO3, PO4, Si04,
- over 20% no Chlorophyll values,
- over 72% do not contain NO2 values
- all stations contain depth information

---> Instead of using FlashWeave with metadata, we go for EnDED - so all station can be kept

## Change format
```{r, eval = FALSE}
ENV_intersection <- t(ENV_intersection)
colnames(ENV_intersection) <- ENV_intersection[1,]
ENV_intersection <- ENV_intersection[-1,]
ENV_intersection <- ENV_intersection[,sort(colnames(ENV_intersection))]
```

## ENV colnames should agree with Euk and Prok
```{r, eval = FALSE}
sum(1*(colnames(ENV_intersection) == colnames(Euk_intersection)))==dim(ENV_intersection)[2]
sum(1*(colnames(ENV_intersection) == colnames(Prok_intersection)))==dim(ENV_intersection)[2]
```
Yes, they do!

## Plot environmental values
```{r}
BREAKS <- 100
hist(as.numeric(ENV_intersection["Depth",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["Temperature",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["Salinity",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["Fluorescence",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["NO3_cruise_and_WOA13",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["PO4_cruise_and_PO4_WOA13",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["SiO4cruise_and_SiO4_WOA13",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["Chlorophyll",]), breaks = BREAKS)
hist(as.numeric(ENV_intersection["NO2",]), breaks = BREAKS)
```

# Filter datasets
## Eukaryotes
-> MalaDeep Euk has another filter size than other datasets
-> however, prevalence is 5%, i.e. 397*0.05=19.85 -> Euk has to be present in at least 20 stations
```{r}
length(grep("MalaDeep",colnames(Euk_intersection)))
```
-> MalaDeep has 13 stations
-> Thus, Euk that may be present because of the bigger filter size and not present in other datasets, will be removed due to the presence filter

Filter ASVs based on their abundance sum and presence.
```{r, eval = FALSE}
paste("Number of ASV in Euk_intersection: ", dim(Euk_intersection)[1], sep="")
paste("Abundance-sum filter (", THRESHOLD_abundancesum, ") removes ", dim(Euk_intersection)[1] - length(which(rowSums(Euk_intersection)>THRESHOLD_abundancesum)),
      " and keeps ", length(which(rowSums(Euk_intersection)>THRESHOLD_abundancesum)), " ASVs", sep="")
paste("Prevalence filter (", THRESHOLD_presence, ") removes ", dim(Euk_intersection)[1] - length(which(rowSums(1*Euk_intersection>0) > dim(Euk_intersection)[2]*THRESHOLD_presence)),
      " and keeps ", length(which(rowSums(1*Euk_intersection>0) > dim(Euk_intersection)[2]*THRESHOLD_presence)), " ASVs", sep="")
paste("Both filter combined remove ", 
      dim(Euk_intersection)[1] - length(which(rowSums(Euk_intersection)>THRESHOLD_abundancesum & rowSums(1*Euk_intersection>0)>dim(Euk_intersection)[2]*THRESHOLD_presence)),
      " and keeps ", 
      length(which(rowSums(Euk_intersection)>THRESHOLD_abundancesum & rowSums(1*Euk_intersection>0)>dim(Euk_intersection)[2]*THRESHOLD_presence)),
      " ASVs", sep="")
Euk_abund100 <- Euk_intersection[which(rowSums(Euk_intersection)>THRESHOLD_abundancesum),]
Euk_core <- Euk_intersection[which(rowSums(Euk_intersection)>THRESHOLD_abundancesum & rowSums(1*Euk_intersection>0)>dim(Euk_intersection)[2]*THRESHOLD_presence),]
```
[1] "Number of ASV in Euk_intersection: 103,421"
[1] "Abundance-sum filter (100) removes 88,328 and keeps 15,093 ASVs"
[1] "Prevalence filter (0.05) removes 100,465 and keeps 2,956 ASVs"
[1] "Both filter combined remove 100,499 and keeps 2,922 ASVs"

## Prokaryotes
```{r, eval = FALSE}
paste("Number of ASV in Prok_intersection: ", dim(Prok_intersection)[1], sep="")
paste("Abundance-sum filter (", THRESHOLD_abundancesum, ") removes ",
      dim(Prok_intersection)[1] - length(which(rowSums(Prok_intersection)>THRESHOLD_abundancesum)),
      " and keeps ", length(which(rowSums(Prok_intersection)>THRESHOLD_abundancesum)), " ASVs", sep="")
paste("Prevalence filter (", THRESHOLD_presence, ") removes ",
      dim(Prok_intersection)[1] - length(which(rowSums(1*Prok_intersection>0) > dim(Prok_intersection)[2]*THRESHOLD_presence)),
      " and keeps ", length(which(rowSums(1*Prok_intersection>0) > dim(Prok_intersection)[2]*THRESHOLD_presence)), " ASVs", sep="")
paste("Both filter combined remove ", 
      dim(Prok_intersection)[1] - length(which(rowSums(Prok_intersection)>THRESHOLD_abundancesum & rowSums(1*Prok_intersection>0)>dim(Prok_intersection)[2]*THRESHOLD_presence)),
      " and keeps ", 
      length(which(rowSums(Prok_intersection)>THRESHOLD_abundancesum & rowSums(1*Prok_intersection>0)>dim(Prok_intersection)[2]*THRESHOLD_presence)),
      " ASVs", sep="")
Prok_abund100 <- Prok_intersection[which(rowSums(Prok_intersection)>THRESHOLD_abundancesum),]
Prok_core <- Prok_intersection[which(rowSums(Prok_intersection)>THRESHOLD_abundancesum & rowSums(1*Prok_intersection>0)>dim(Prok_intersection)[2]*THRESHOLD_presence),]
```
[1] "Number of ASV in Prok_intersection: 50,762"
[1] "Abundance-sum filter (100) removes 39,937 and keeps 10,825 ASVs"
[1] "Prevalence filter (0.05) removes 48,209 and keeps 2,553 ASVs"
[1] "Both filter combined remove 48,227 and keeps 2,535 ASVs"

## Number of reads kept after filtering
How many reads remain if abundance filter is applied?
```{r, eval = FALSE}
paste("Euk: The filtering meant removing ", dim(Euk_intersection)[1], " - ", dim(Euk_abund100)[1], " = ",
      dim(Euk_intersection)[1]-dim(Euk_abund100)[1], " of the rare ASVs, which removed ",
      sum(Euk_intersection)-sum(Euk_abund100), " reads from the total of ", sum(Euk_intersection),
      " reads. Thus ", sum(Euk_abund100), " (", sum(Euk_abund100)/sum(Euk_intersection)*100, "%) reads for ",
      dim(Euk_abund100)[1], " ASVs remain.", sep="")

paste("Prok: The filtering meant removing ", dim(Prok_intersection)[1], " - ", dim(Prok_abund100)[1], " = ",
      dim(Prok_intersection)[1]-dim(Prok_abund100)[1], " of the rare ASVs, which removed ",
      sum(Prok_intersection)-sum(Prok_abund100), " reads from the total of ", sum(Prok_intersection), " reads. Thus ",
      sum(Prok_abund100), " (", sum(Prok_abund100)/sum(Prok_intersection)*100,
      "%) reads for ", dim(Prok_abund100)[1], " ASVs remain.", sep="")
```
[1] "Euk: The filtering meant removing 103421 - 15093 = 88328 of the rare ASVs, which removed 898771 reads from the total of 45461199 reads. Thus 44562428 (98.0229931903028%) reads for 15093 ASVs remain."
[1] "Prok: The filtering meant removing 50762 - 10825 = 39937 of the rare ASVs, which removed 634081 reads from the total of 31425163 reads. Thus 30791082 (97.9822507205452%) reads for 10825 ASVs remain."

How many reads remain if both filter are applied?
```{r, eval = FALSE}
paste("The filtering meant removing ", dim(Euk_intersection)[1], " - ", dim(Euk_core)[1], " = ",
      dim(Euk_intersection)[1]-dim(Euk_core)[1], " of the rare ASVs, which removed ",
      sum(Euk_intersection)-sum(Euk_core), " reads from the total of ", sum(Euk_intersection), " reads. Thus ",
      sum(Euk_core), " (", sum(Euk_core)/sum(Euk_intersection)*100, "%) reads for ",
      dim(Euk_core)[1], " ASVs remain.", sep="")

paste("The filtering meant removing ", dim(Prok_intersection)[1], " - ", dim(Prok_core)[1], " = ",
      dim(Prok_intersection)[1]-dim(Prok_core)[1], " of the rare ASVs, which removed ",
      sum(Prok_intersection)-sum(Prok_core), " reads from the total of ", sum(Prok_intersection), " reads. Thus ",
      sum(Prok_core), " (", sum(Prok_core)/sum(Prok_intersection)*100, "%) reads for ",
      dim(Prok_core)[1], " ASVs remain.", sep="")
```
[1] "The filtering meant removing 103421 - 2922 = 100499 of the rare ASVs, which removed 9188523 reads from the total of 45461199 reads. Thus 36272676 (79.788207961695%) reads for 2922 ASVs remain."
[1] "The filtering meant removing 50762 - 2535 = 48227 of the rare ASVs, which removed 4774995 reads from the total of 31425163 reads. Thus 26650168 (84.8051862133539%) reads for 2535 ASVs remain."

# clr-transformation
```{r}
# Function to compute Central log ratio transformation and return result as a vector
my_clr <- function(x) {as.vector( clr(x))}

# Add pseudo count of 0.001 and Central log ratio transformation
Euk_clr <- dplyr::mutate_at((Euk_core + pseudo_count), colnames(Euk_core), my_clr)
Prok_clr <- dplyr::mutate_at((Prok_core + pseudo_count), colnames(Prok_core), my_clr)
```

# merge tables
```{r}
ASV_abund100 <- rbind(Euk_abund100, Prok_abund100)
ID_abund100 <- c(paste("Euk_",rownames(Euk_abund100),sep=""), paste("Prok_",rownames(Prok_abund100),sep=""))

ASV <- rbind(Euk_core, Prok_core)
ASV_clr <- rbind(Euk_clr, Prok_clr)
ID <- c(paste("Euk_",rownames(Euk_core),sep=""), paste("Prok_",rownames(Prok_core),sep=""))
```

# Save tables
```{r, eval = FALSE}
path <- paste(PATH,"00_Tables/",sep="")
filename <- "ASV_abund100.txt"
write.table(cbind(ID_abund100,ASV_abund100),paste(path,filename,sep=""),sep="\t",quote=FALSE,
            row.names=FALSE,col.names=c("ID",colnames(ASV_abund100)))

filename <- "ASV.txt"
write.table(cbind(ID,ASV),paste(path,filename,sep=""),sep="\t",quote=FALSE,
            row.names=FALSE,col.names=c("ID",colnames(ASV)))

filename <- "clr_ASV.tsv"
write.table(cbind(ID,ASV_clr),paste(path,filename,sep=""),sep="\t",quote=FALSE,
            row.names=FALSE,col.names=c("ID",colnames(ASV_clr)))

filename <- 'ENV.txt'
ID <- paste("ENV_", rownames(ENV_intersection), sep ="")
write.table(cbind(ID,ENV_intersection),paste(path,filename,sep=""),sep="\t",quote=FALSE,
            row.names=FALSE,col.names=c("ID",colnames(ENV_intersection)))
```