---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Distribution of Samples
## Required Packages
```{r}
library(igraph)
library(ggplot2)
library(ggridges)
library(reshape)
library(RColorBrewer)
library(circlize)
library(tidyr)
theme_set(theme_minimal())
```

## Parameter
```{r}
PATH <- "/GlobalNetworkMalaspinaHotmix/"
PATH <- "/Users/ina/Dropbox/DATA/Project_GlobalOcean_2021_March/GitHub/"
```

## Read in file
```{r}
path <- paste(PATH,"00_Tables/",sep="")
filename <- "Sample_Classification.tsv"
samples <- read.table(paste(path,filename,sep=""), header = TRUE)
rownames(samples) <- samples$Sample
```

## Number of samples in regions and depth layers
```{r}
for(id in c("SRF", "EPI", "DCM", "MES", "BAT"))
{
  print(paste(id,length(which(samples$layer==id))))
}
table(samples$OceanRegion)
table(samples[,c("layer","OceanRegion")])
```
[1] "SRF 157"
[1] "EPI 22"
[1] "DCM 38"
[1] "MES 91"
[1] "BAT 89"

 IO  MS NAO NPO SAO SPO 
 53 145  78  53  47  21 
     OceanRegion
layer IO MS NAO NPO SAO SPO
  BAT  8 35  20  12  11   3
  DCM  3 21   6   3   4   1
  EPI  0 18   4   0   0   0
  MES  7 52  14   9   6   3
  SRF 35 19  34  29  26  14

## Latitude and Longitude
```{r}
summary(samples$Latitude)
summary(samples$Longitude)
```
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 -40.55  -13.53   21.89   12.59   35.95   41.49 
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-179.524  -32.837    0.968  -14.154   21.372  179.141 

## Depth range per layer
```{r}
summary(samples$depth[samples$layer=="SRF"])
summary(samples$depth[samples$layer=="EPI"])
summary(samples$depth[samples$layer=="DCM"])
summary(samples$depth[samples$layer=="MES"])
summary(samples$depth[samples$layer=="BAT"])
```
Surface
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  3.000   3.000   3.000   3.025   3.000   5.000 
  
Epipelagic (neither surface nor DCM)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  12.00   50.00   50.00   46.45   50.00   50.00 

DCM
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  37.00   75.00   86.00   89.16  110.00  130.00 

Mesopelagic
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  200.0   400.0   550.0   558.5   765.0  1000.0 
  
Bathypelagic
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   1065    2000    2421    2600    3518    4539 
   
## Map
Showing stations on the map
```{r}
world_map <- map_data("world")
p <- ggplot(world_map, aes(x = long, y = lat, group = group)) +
       geom_polygon(fill="lightgray", colour = "white") +
       theme_classic() +
       theme(text = element_text(size = 12)) +
       geom_point(data = samples, aes(x = Longitude, y = Latitude, group="cluster"), shape=15, color = "black", alpha = 0.6, size = 1) +
       facet_grid(factor(layer,levels=c("SRF","EPI","DCM","MES","BAT"))~.)
path <- paste(PATH,"01_Metadata/",sep="")
filaname <- "Map.png"
ggsave(paste(path,filename,sep=""), width = 3.5, height = 7, units = "in", plot = p)
```