---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Global network metrics
## Required Packages
```{r, echo=FALSE}
library(igraph)
library(tnet)    # https://toreopsahl.com/2010/03/20/closeness-centrality-in-networks-with-disconnected-components/
library(ggplot2)
library(reshape2)
theme_set(theme_minimal())
```

## parameter and data
```{r}
PATH <- "GlobalNetworkMalaspinaHotmix/"
path <- paste(PATH,"02_NetworkConstruction/",sep="")
filename <- "SampleSpecificSubnetworks.tsv"
NW <- read.table(paste(path,filename,sep=""), header = TRUE, stringsAsFactors = FALSE)
G <- graph_from_edgelist(as.matrix(NW[,c("Source","Target")]))
vcount(G)
ecount(G)
```
5448 nodes and 29118 edges

## function: get_nw_properties(dt)
```{r}
get_nw_proterties <- function(dt, col_associationScore, ID){
  parameters <- c('num_nodes', 'num_edges', 'edge_density', 'num_pos_edges', 'portion_pos_edges', 'num_neg_edges', 'portion_neg_edges',
                  'average_pos_association_strength','average_neg_association_strength',
                  'transitivity_global_clusering_coef', 'transitivity_ave_clustering_coef_mean_local',
                  'ave_path_length', 'diameter', 'mean_degree', 'degreecentralization',
                  'assortativity_nominal_EukProk', 'assortativity_degree',
                  'ave_node_betweenness', 'ave_edge_betweenness', 'betweennesscentralization',
                  'ave_closeness', 'closenesscentralization', 'closenesscentralization_disconnected_graphs', 'closenesscentralization_disconnected_graphs_normalized')

  NWpropOverview <- data.frame(newNW = rep(0, length(parameters)))
  rownames(NWpropOverview) <- parameters

  # new entry
  NWpropOverview$newNW

  # Create igraph object
  G <- graph_from_data_frame(dt, directed = FALSE)

  # number of nodes without isolated nodes
  NWpropOverview['num_nodes', 'newNW'] <- vcount(G)

  # number of edges (`num_edges`) 
  NWpropOverview['num_edges', 'newNW'] <- ecount(G)

  # edge density (`edge_density`): The proportion of present edges from all possible edges in the network.
  NWpropOverview['edge_density', 'newNW'] <- edge_density(simplify(G), loops = FALSE)

  # number of positive edges (`num_pos_edges`)
  NWpropOverview['num_pos_edges', 'newNW'] <- sum(dt[,col_associationScore]>0)

  # percentage of postive edges (`portion_pos_edges`)
  NWpropOverview['portion_pos_edges', 'newNW'] <- NWpropOverview['num_pos_edges', 'newNW'] / NWpropOverview['num_edges', 'newNW']

  # number of negativee edges (`num_neg_edges`)
  NWpropOverview['num_neg_edges', 'newNW'] <- sum(dt[,col_associationScore]<0)

  # percentage of negative edges (`portion_neg_edges`)
  NWpropOverview['portion_neg_edges', 'newNW'] <- NWpropOverview['num_neg_edges', 'newNW'] / NWpropOverview['num_edges', 'newNW']
  
  # average positive association strength (`average_pos_association_strength`)
  NWpropOverview['average_pos_association_strength', 'newNW'] <- mean(dt[dt[,col_associationScore]>0,col_associationScore])
  
  # average negative association stength (`average_neg_association_strength`)
  NWpropOverview['average_neg_association_strength', 'newNW'] <- mean(dt[dt[,col_associationScore]<0,col_associationScore])

  # transitivity of a graph
  NWpropOverview['transitivity_global_clusering_coef', 'newNW'] <- transitivity(G, type="global")
  NWpropOverview['transitivity_ave_clustering_coef_mean_local', 'newNW'] <- transitivity(G, type="average")

  # average path length (`ave_path_length`): Average path length: the mean of the shortest distance between each pair of nodes in the network (in both directions for directed graphs).
  NWpropOverview['ave_path_length', 'newNW'] <- average.path.length(G, directed = FALSE, unconnected = TRUE)
  # mean_distance(g, directed=F) would also work

  # diameter (`diameter`): longest shortest path between two nodes in the network.
  NWpropOverview['diameter', 'newNW'] <- diameter(G, directed = FALSE, weights=NA)

  # average degree (`ave_degree`) (for each node-> histogram) (degree distribution)
  NWpropOverview['mean_degree', 'newNW'] <- mean(igraph::degree(G, mode="all"))

  # degreecentralization
  NWpropOverview['degreecentralization', 'newNW'] <- centr_degree(G, mode="all", normalized=T)$centralization

  # assortativity_nominal_EukProk
  types <- substr(V(G)$name,1,3)
  types[which(types=="Euk")] <- 1
  types[which(types=="Pro")] <- 2
  NWpropOverview['assortativity_nominal_EukProk', 'newNW'] <- assortativity_nominal(G, types, directed = FALSE)

  # assortativity_degree
  NWpropOverview['assortativity_degree', 'newNW'] <- assortativity_degree(G, directed = FALSE)

  #Betweenness (centrality based on a broker position connecting others)
  #Number of geodesics that pass through the node or the edge.
  # average betweenness (`ave_betweenness`)
  NWpropOverview['ave_node_betweenness', 'newNW'] <- mean(betweenness(G, directed = FALSE, weights = NA))
  NWpropOverview['ave_edge_betweenness', 'newNW'] <- mean(edge_betweenness(G, directed = FALSE, weights = NA))
  # betweennesscentralization
  NWpropOverview['betweennesscentralization', 'newNW'] <- centr_betw(G, directed = FALSE, normalized=T)$centralization

  #Closeness (centrality based on distance to others in the graph)
  #Inverse of the node???s average geodesic distance to others in the ig.sparccwork.
  # average closeness (`ave_closeness`)
  NWpropOverview['ave_closeness', 'newNW'] <- mean(closeness(G, mode = "all", weights = NA))

  # closenesscentralization
  NWpropOverview['closenesscentralization', 'newNW'] <- centr_clo(G, mode = "all", normalized=T)$centralization

  # closenesscentralization_disconnected_graphs
  # The network might be undirected. If this is the case, each tie should be mention twice. The symmetrise-function can be used to include reverse version of each tie. -> Thus, each edge is added twice: both ways!
  ID_mapping <- data.frame(ID=c(1:vcount(G)))
  rownames(ID_mapping) <- V(G)$name
  net <- rbind(cbind(i=ID_mapping[dt$Source,"ID"],j=ID_mapping[dt$Target,"ID"],w=rep(1,length(ID_mapping[dt$Source,"ID"]))),
               cbind(i=ID_mapping[dt$Target,"ID"],j=ID_mapping[dt$Source,"ID"],w=rep(1,length(ID_mapping[dt$Source,"ID"]))))

  Closeness_alternative <- closeness_w(net, gconly = FALSE)
  NWpropOverview['closenesscentralization_disconnected_graphs', 'newNW'] <- mean(Closeness_alternative[,"closeness"])
  NWpropOverview['closenesscentralization_disconnected_graphs_normalized', 'newNW'] <- mean(Closeness_alternative[,"n.closeness"]) 

  # update ID
  colnames(NWpropOverview)[which(colnames(NWpropOverview)=="newNW")] <- ID

  return(NWpropOverview)
}
```

## global metrics for static nw
```{r}
NWprop_static <- get_nw_proterties(NW[,c(1:3)], "Weight", "staticNW")
NWprop_static <- t(NWprop_static)
NWprop_static <- cbind(rownames(NWprop_static),NWprop_static)
colnames(NWprop_static)[1] <- "Sample"
```

## global metrics for sample-specific subnetworks
```{r}
COLNAMES <- colnames(NW)[grep("_",colnames(NW))]
NWprop <- get_nw_proterties(NW[which(NW[,COLNAMES[1]]==1),], "Weight", COLNAMES[1])

for(i in c(2:length(COLNAMES)))
{
  NWpropnew <- get_nw_proterties(NW[which(NW[,COLNAMES[i]]==1),], "Weight", COLNAMES[i])
  NWprop <- cbind(NWprop, NWpropnew)
}

NWprop <- t(NWprop)
NWprop <- cbind(rownames(NWprop),NWprop)
colnames(NWprop)[1] <- "Sample"
```

## Save tables
```{r}
path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
filename <- "NW_properties_overview_staticNW.tsv"
write.table(NWprop_static, paste(path,file,sep=""), row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t", dec = ".")
filename <- "NW_properties_overview_sampleSpecificNW.tsv"
write.table(NWprop, paste(path,file,sep=""), row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t", dec = ".")
```

## Visualization
### Read in files
```{r}
path <- paste(PATH,"00_Tables/",sep="")
filename <- "Sample_Classification.tsv"
SAM <- read.table(paste(path,filename,sep=""), header = TRUE)

path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
filename <- "NW_properties_overview_sampleSpecificNW.tsv"
NWprop <- read.table(paste(path,filename,sep=""), header = TRUE)
```

### Boxplot
```{r}
NWid <- c("num_nodes", "num_edges", "edge_density", "average_pos_association_strength", "transitivity_global_clusering_coef", "ave_path_length", "assortativity_nominal_EukProk", "assortativity_degree")

dt_temp <- merge(NWprop[,c("Sample",NWid)],SAM[,c("Sample","layer","OceanRegion")], by="Sample", all=TRUE)
dt_temp <- melt(dt_temp)
p <- ggplot(dt_temp, aes(x=factor(layer, levels = c("SRF","EPI","DCM","MES","BAT")), y=value)) + geom_violin() + geom_boxplot(width=0.1) +
             xlab("") + ylab("") + theme_classic() +
             theme(text = element_text(size = 12)) +
             facet_grid(variable~., scales = "free")
path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
filename <- "GlobalMetrics_Layer.pdf"
ggsave(paste(path,filename,sep=""), plot=p, width=4,height=8)
```

### Exclude outlier for better visualization
Sample num_nodes num_edges edge_density average_pos_association_strength transitivity_global_clusering_coef ave_path_length assortativity_nominal_EukProk assortativity_degree layer
366 MalaVP_DNA_D2795_4000m        32        37   0.07459677                        0.2238359                          0.1666667        2.995536                     0.6525822           0.08808081   BAT
    OceanRegion
366         NAO
-> this edge density will be set to "NA" for visualization purposes!
```{r}
NWid <- c("num_nodes", "num_edges", "edge_density", "average_pos_association_strength", "transitivity_global_clusering_coef", "ave_path_length", "assortativity_nominal_EukProk", "assortativity_degree")

dt_temp <- merge(NWprop[,c("Sample",NWid)],SAM[,c("Sample","layer","OceanRegion")], by="Sample", all=TRUE)
dt_temp[which(dt_temp$edge_density>0.05),]
dt_temp[which(dt_temp$edge_density>0.05),"edge_density"] <- NA
dt_temp <- melt(dt_temp)
p <- ggplot(dt_temp, aes(x=factor(layer, levels = c("SRF","EPI","DCM","MES","BAT")), y=value)) + geom_violin() + geom_boxplot(width=0.1) +
             xlab("") + ylab("") + theme_classic() +
             theme(text = element_text(size = 12)) +
             facet_grid(variable~., scales = "free")
path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
filename <- "GlobalMetrics_Layer_edgeDensity_missingValueForMax0.7.pdf"
ggsave(paste(path,filename,sep=""), plot=p, width=4,height=8)
```

### Boxplot for each Layer
```{r}
dt_temp <- merge(NWprop[,c("Sample",NWid)],SAM[,c("Sample","layer","OceanRegion")], by="Sample", all=TRUE)
dt_temp[which(dt_temp$edge_density>0.05),"edge_density"] <- NA
dt_temp <- melt(dt_temp)
path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
for(i in c("SRF","EPI","DCM","MES","BAT"))
{
  p <- ggplot(dt_temp[which(dt_temp$layer==i),], aes(x=factor(OceanRegion, levels = c("MS","NAO","SAO","SPO","NPO","IO")), y=value)) + geom_violin() + geom_boxplot(width=0.1) +
             xlab("") + ylab("") + theme_classic() +
             theme(text = element_text(size = 12)) +
             facet_grid(variable~., scales = "free")
 filename <- paste("GlobalMetrics_DiffRegions_",i,".pdf",sep="")
 ggsave(paste(path,filename,sep=""), plot=p, width=4,height=8)
}
```

### Boxplot including Layer and Region
```{r}
dt_temp <- merge(NWprop[,c("Sample",NWid)],SAM[,c("Sample","layer","OceanRegion")], by="Sample", all=TRUE)
dt_temp[which(dt_temp$edge_density>0.05),"edge_density"] <- NA
dt_temp <- melt(dt_temp)

 p <- ggplot(dt_temp, aes(x=factor(layer, levels = c("SRF","DCM","MES","BAT")), y=value)) + geom_violin() + geom_boxplot(width=0.1) +
             xlab("") + ylab("") + theme_classic() +
             theme(text = element_text(size = 12)) +
             facet_grid(variable~factor(OceanRegion, levels = c("MS","NAO","SAO","SPO","NPO","IO")), scales = "free")
 path <- paste(PATH,"03_GlobalNetworkMetrics/",sep="")
 filename <- paste("GlobalMetrics_DiffRegions_Layer_edgeDensity_missingValueForMax0.7.pdf",sep="")
 ggsave(paste(path,filename,sep=""), plot=p, width=12, height=14)
```

## Stats
Number nodes and edges
```{r}
summary(NWprop$num_nodes)
summary(NWprop$num_edges)
```
number of nodes
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   32.0   408.0   562.0   592.4   758.0  1306.0 
  
number od egdes
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
     37     968    1554    1776    2352    5598 
   
```{r}
hist(NWprop$num_nodes, breaks=100)
hist(NWprop$num_edges, breaks=100)
hist(NWprop$edge_density, breaks=100)
```

Other metrics
```{r}
summary(NWprop$edge_density)
summary(NWprop$transitivity_global_clusering_coef)
summary(NWprop$ave_path_length)
summary(NWprop$assortativity_degree)
summary(NWprop$assortativity_nominal_EukProk)
summary(NWprop$average_pos_association_strength)
```
> summary(NWprop$edge_density)
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.004770 0.008320 0.009735 0.010703 0.012138 0.074597 

> summary(NWprop$transitivity_global_clusering_coef)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.02089 0.03576 0.04749 0.04720 0.05484 0.16667 

> summary(NWprop$ave_path_length)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  2.996   4.211   4.471   4.647   4.930   9.082 
  
> summary(NWprop$assortativity_degree)
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-0.05335  0.17069  0.21918  0.20926  0.25530  0.38482

> summary(NWprop$assortativity_nominal_EukProk)
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max.     NA's 
-0.01869  0.77821  0.83933  0.81124  0.87959  1.00000        1  

> summary(NWprop$average_pos_association_strength)
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.1775  0.1892  0.1984  0.1981  0.2059  0.2412 