---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Association prevalence
## Required Packages
```{r, echo=FALSE}
library(igraph)
library(ggplot2)
theme_set(theme_minimal())
library(reshape)
library(dplyr)
library(RColorBrewer)
library(circlize)
```

## parameter and data
```{r}
PATH <- "GlobalNetworkMalaspinaHotmix/"

path <- paste(PATH,"00_Tables/",sep="")
filename <- "Sample_Classification.tsv"
SAM <- read.table(paste(path,filename,sep=""), header = TRUE)

path <- paste(PATH,"02_NetworkConstruction/",sep="")
filename <- "SampleSpecificSubnetworks.tsv"
NW <- read.table(paste(path,filename,sep=""), header = TRUE, stringsAsFactors = FALSE)
G <- graph_from_edgelist(as.matrix(NW[,c("Source","Target")]))
vcount(G)
ecount(G)
```
5448 nodes and 29118 edges

## overall prevalence
```{r}
NW$EdgePrevalence <- rowSums(NW[,-c(1:3)], na.rm = TRUE)/dim(NW[,-c(1:3)])[2]
hist(NW$EdgePrevalence, breaks = 100)
```

```{r}
summary(NW$EdgePrevalence)
```
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.00000 0.03023 0.04534 0.06101 0.07305 0.66499 

## Prevalence within oceanic region and depth layer
```{r}
PREV <- NW[,c("Source","Target","EdgePrevalence")]
IDs <- c(paste("MS",c("SRF", "EPI", "DCM", "MES", "BAT"),sep="_"),
         paste("NAO",c("SRF", "EPI", "DCM", "MES", "BAT"),sep="_"),
         paste("SAO",c("SRF", "DCM", "MES", "BAT"),sep="_"),
         paste("SPO",c("SRF", "DCM", "MES", "BAT"),sep="_"),
         paste("NPO",c("SRF", "DCM", "MES", "BAT"),sep="_"),
         paste("IO",c("SRF", "DCM", "MES", "BAT"),sep="_"))
for(i in IDs)
{
  if(length(which(SAM$OceanRegion_Layer==i))>1)
  {
    PREV[,paste("Prevalence",i,sep="_")] <- rowSums(NW[,as.character(SAM$Sample[which(SAM$OceanRegion_Layer==i)])], na.rm = TRUE)/length(which(SAM$OceanRegion_Layer==i))
  }else{
    PREV[,paste("Prevalence",i,sep="_")] <- NW[,as.character(SAM$Sample[which(SAM$OceanRegion_Layer==i)])]
  }
}
```

## Save
```{r}
path <- paste(PATH,"04_Prevalence/",sep="")
filename <- "EdgePrevalence.tsv"
write.table(PREV, paste(path,filename,sep=""), col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE)
```

## Visualization
```{r}
colnames(PREV)
p <- ggplot(PREV, aes(x=EdgePrevalence)) + geom_histogram(binwidth=0.01) +
           ylab("Frequency") + xlab("Jaccard index (Spatial recurrence)") +
           theme_classic() + theme(text = element_text(size = 12))
path <- paste(PATH,"04_Prevalence/",sep="")
filename <- "Prevalence_all_JaccardIndex_SpatialRecurrence.pdf"
ggsave(paste(path,filename,sep=""), width = 8, height = 4, plot = p)

dt_temp <- melt(PREV[,c(paste("Prevalence_MS", c("SRF","EPI","DCM","MES","BAT"),sep="_"),
                        paste("Prevalence_NAO", c("SRF","EPI","DCM","MES","BAT"),sep="_"),
                        paste("Prevalence_SAO", c("SRF","DCM","MES","BAT"),sep="_"),
                        paste("Prevalence_SPO", c("SRF","DCM","MES","BAT"),sep="_"),
                        paste("Prevalence_NPO", c("SRF","DCM","MES","BAT"),sep="_"),
                        paste("Prevalence_IO", c("SRF","DCM","MES","BAT"),sep="_"))])
dt_temp$RegionDepthLayer <- gsub("Prevalence_","",dt_temp$variable)
unique(dt_temp$RegionDepthLayer)
dt_temp$DepthLayer <- gsub("_","",substr(dt_temp$RegionDepthLayer,4,7))
unique(dt_temp$DepthLayer)
dt_temp$Region <- gsub("_","",substr(dt_temp$RegionDepthLayer,1,3))
unique(dt_temp$Region)
head(dt_temp)
p <- ggplot(dt_temp, aes(x=value)) + geom_histogram(binwidth=0.05) + scale_x_continuous(breaks=seq(0,1,0.2)) +
           ylab("Frequency") + xlab("Association prevalence (Spatial recurrence)") + 
           theme_bw() + theme(text = element_text(size = 12)) +
           facet_grid(factor(DepthLayer,levels=c("SRF","EPI","DCM","MES","BAT"))~factor(Region,levels=c("MS","NAO","SAO","SPO","NPO","IO")))
path <- paste(PATH,"04_Prevalence/",sep="")
filename <- "Prevalence_HorizontalConnectivity_JaccardIndex_SpatialRecurrence_Regions_DepthLayers.pdf"
ggsave(paste(path,filename,sep=""), width = 10, height = 4, plot = p)

dt_temp <- dt_temp[which(dt_temp$value!=0),]
p <- ggplot(dt_temp, aes(x=value)) + geom_histogram(binwidth=0.05) + scale_x_continuous(breaks=seq(0,1,0.2)) +
           ylab("Frequency") + xlab("Association prevalence (Spatial recurrence)") + 
           theme_bw() + theme(text = element_text(size = 12)) +
           facet_grid(factor(DepthLayer,levels=c("SRF","EPI","DCM","MES","BAT"))~factor(Region,levels=c("MS","NAO","SAO","SPO","NPO","IO")))
path <- paste(PATH,"04_Prevalence/",sep="")
filename <- "Prevalence_HorizontalConnectivity_JaccardIndex_SpatialRecurrence_Regions_DepthLayers_withoutZero.pdf"
ggsave(paste(path,filename,sep=""), width = 10, height = 4, plot = p)
```


## Number of prevalent associations
How many 100%?
```{r}
colSums(1*(PREV[,-c(1,2)]==1))
```
    EdgePrevalence  Prevalence_MS_SRF  Prevalence_MS_EPI  Prevalence_MS_DCM  Prevalence_MS_MES  Prevalence_MS_BAT Prevalence_NAO_SRF Prevalence_NAO_EPI Prevalence_NAO_DCM Prevalence_NAO_MES Prevalence_NAO_BAT 
                 0                 35                 21                 18                  0                 13                  5                824                 18                  0                  0 
Prevalence_SAO_SRF Prevalence_SAO_DCM Prevalence_SAO_MES Prevalence_SAO_BAT Prevalence_SPO_SRF Prevalence_SPO_DCM Prevalence_SPO_MES Prevalence_SPO_BAT Prevalence_NPO_SRF Prevalence_NPO_DCM Prevalence_NPO_MES 
                 4                418                 67                 35                 40               1530                399                217                  5                557                 37 
Prevalence_NPO_BAT  Prevalence_IO_SRF  Prevalence_IO_DCM  Prevalence_IO_MES  Prevalence_IO_BAT 
                22                  4                942                 58                 41 
                
Above 70%?
```{r}
colSums(1*(PREV[,-c(1,2)]>0.7))
```
    EdgePrevalence  Prevalence_MS_SRF  Prevalence_MS_EPI  Prevalence_MS_DCM  Prevalence_MS_MES  Prevalence_MS_BAT Prevalence_NAO_SRF Prevalence_NAO_EPI Prevalence_NAO_DCM Prevalence_NAO_MES Prevalence_NAO_BAT 
                 0                324                307                211                178                338                297               1593                212                147                 38 
Prevalence_SAO_SRF Prevalence_SAO_DCM Prevalence_SAO_MES Prevalence_SAO_BAT Prevalence_SPO_SRF Prevalence_SPO_DCM Prevalence_SPO_MES Prevalence_SPO_BAT Prevalence_NPO_SRF Prevalence_NPO_DCM Prevalence_NPO_MES 
               133               1258                143                120                459               1530                399                217                493                557                159 
Prevalence_NPO_BAT  Prevalence_IO_SRF  Prevalence_IO_DCM  Prevalence_IO_MES  Prevalence_IO_BAT 
               354                336                942                363                123 

Above 0%?
```{r}
colSums(1*(PREV[,-c(1,2)]>0))
```
    EdgePrevalence  Prevalence_MS_SRF  Prevalence_MS_EPI  Prevalence_MS_DCM  Prevalence_MS_MES  Prevalence_MS_BAT Prevalence_NAO_SRF Prevalence_NAO_EPI Prevalence_NAO_DCM Prevalence_NAO_MES Prevalence_NAO_BAT 
             28442               3263               4196               4736               7336               3694              13478               3027               3738               5689               6831 
Prevalence_SAO_SRF Prevalence_SAO_DCM Prevalence_SAO_MES Prevalence_SAO_BAT Prevalence_SPO_SRF Prevalence_SPO_DCM Prevalence_SPO_MES Prevalence_SPO_BAT Prevalence_NPO_SRF Prevalence_NPO_DCM Prevalence_NPO_MES 
             11026               4199               3740               3886              10420               1530               2066               3159              11919               3100               3781 
Prevalence_NPO_BAT  Prevalence_IO_SRF  Prevalence_IO_DCM  Prevalence_IO_MES  Prevalence_IO_BAT 
              4834              11736               3411               4344               2790  

## Highly prevalent associations             
Chord Diagram for >70% association prevalence per depth and region

### Assign taxonomy
```{r}
path <- paste(PATH,"00_Tables/",sep="")
filename <- "Euk_taxdata.txt"
TAX <- read.table(paste(path,filename,sep=""), header = TRUE, sep = "\t", stringsAsFactors = FALSE)
rownames(TAX) <- TAX$ID
colnames(TAX)
NW$Source_PhylumDivision <- NA
NW$Target_PhylumDivision <- NA
NW$Source_PhylumDivision[which(substr(NW$Source,1,1)=="E")] <- TAX[as.character(NW$Source[which(substr(NW$Source,1,1)=="E")]),"Division_pr2"]
NW$Target_PhylumDivision[which(substr(NW$Target,1,1)=="E")] <- TAX[as.character(NW$Target[which(substr(NW$Target,1,1)=="E")]),"Division_pr2"]
unique(c(as.character(NW$Source_PhylumDivision), as.character(NW$Target_PhylumDivision)))

filename <- "Prok_taxdata.txt"
TAX <- read.table(paste(path,filename,sep=""), header = TRUE, sep = "\t", stringsAsFactors = FALSE)
rownames(TAX) <- TAX$ID
colnames(TAX)
NW$Source_PhylumDivision[which(substr(NW$Source,1,1)=="P")] <- TAX[as.character(NW$Source[which(substr(NW$Source,1,1)=="P")]),"Phylum_SILVA"]
NW$Target_PhylumDivision[which(substr(NW$Target,1,1)=="P")] <- TAX[as.character(NW$Target[which(substr(NW$Target,1,1)=="P")]),"Phylum_SILVA"]
unique(c(as.character(NW$Source_PhylumDivision), as.character(NW$Target_PhylumDivision)))

# Proteobacteria
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Proteobacteria")] <- TAX[as.character(NW$Source[which(NW$Source_PhylumDivision=="Proteobacteria")]),"Class_SILVA"]
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Proteobacteria")] <- TAX[as.character(NW$Target[which(NW$Target_PhylumDivision=="Proteobacteria")]),"Class_SILVA"]

# Kingdom
filename <- "Euk_taxdata.txt"
TAX <- read.table(paste(path,filename,sep=""), header = TRUE, sep = "\t", stringsAsFactors = FALSE)
rownames(TAX) <- TAX$ID
colnames(TAX)
NW$Source_Kingdom <- NA
NW$Target_Kingdom <- NA
NW$Source_Kingdom[which(substr(NW$Source,1,1)=="E")] <- TAX[as.character(NW$Source[which(substr(NW$Source,1,1)=="E")]),"Kingdom_pr2"]
NW$Target_Kingdom[which(substr(NW$Target,1,1)=="E")] <- TAX[as.character(NW$Target[which(substr(NW$Target,1,1)=="E")]),"Kingdom_pr2"]

filename <- "Prok_taxdata.txt"
TAX <- read.table(paste(path,filename,sep=""), header = TRUE, sep = "\t", stringsAsFactors = FALSE)
rownames(TAX) <- TAX$ID
colnames(TAX)
NW$Source_Kingdom[which(substr(NW$Source,1,1)=="P")] <- TAX[as.character(NW$Source[which(substr(NW$Source,1,1)=="P")]),"Kingdom_SILVA"]
NW$Target_Kingdom[which(substr(NW$Target,1,1)=="P")] <- TAX[as.character(NW$Target[which(substr(NW$Target,1,1)=="P")]),"Kingdom_SILVA"]
unique(c(as.character(NW$Source_Kingdom), as.character(NW$Target_Kingdom)))

# Nitrospinae and Nitrospirae
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Nitrospinae")] <- "NiN"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Nitrospinae")] <- "NiN"
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Nitrospirae")] <- "NiR"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Nitrospirae")] <- "NiR"

# Marinimicrobia_(SAR406_clade)
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Marinimicrobia_(SAR406_clade)")] <- "SAR406"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Marinimicrobia_(SAR406_clade)")] <- "SAR406"

# Chlamydiae and Chloroflexi
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Chlamydiae")] <- "ChA"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Chlamydiae")] <- "ChA"
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Chloroflexi")] <- "ChO"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Chloroflexi")] <- "ChO"

# unclassified Bacteria
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="WPS-2")] <- "unBac"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="WPS-2")] <- "unBac"
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="PAUC34f")] <- "unBac"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="PAUC34f")] <- "unBac"
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="AncK6")] <- "unBac"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="AncK6")] <- "unBac"
NW$Source_PhylumDivision[which((is.na(NW$Source_PhylumDivision))&NW$Source_Kingdom=="Bacteria")] <- "unBac"
NW$Target_PhylumDivision[which((is.na(NW$Target_PhylumDivision))&NW$Target_Kingdom=="Bacteria")] <- "unBac"

# unclassified Eukaryota
NW$Source_PhylumDivision[which(NW$Source_PhylumDivision=="Eukaryota_XX")] <- "unEuk"
NW$Target_PhylumDivision[which(NW$Target_PhylumDivision=="Eukaryota_XX")] <- "unEuk"
NW$Source_PhylumDivision[which((is.na(NW$Source_PhylumDivision)) & NW$Source_Kingdom=="Eukaryota")] <- "unEuk"
NW$Target_PhylumDivision[which((is.na(NW$Target_PhylumDivision)) & NW$Target_Kingdom=="Eukaryota")] <- "unEuk"

# unclassified Arch?
NW$Source_PhylumDivision[which((is.na(NW$Source_PhylumDivision))&NW$Source_Kingdom=="Archaea")]
NW$Target_PhylumDivision[which((is.na(NW$Target_PhylumDivision))&NW$Target_Kingdom=="Archaea")]

# any NA left?
NW[which(is.na(NW$Source_Kingdom)),"Source_Kingdom"] <- substr(NW[which(is.na(NW$Source_Kingdom)),"Source"],1,3)
NW[which(is.na(NW$Target_Kingdom)),"Target_Kingdom"] <- substr(NW[which(is.na(NW$Target_Kingdom)),"Target"],1,3)
NW[which(NW$Source_Kingdom=="Euk"),"Source_Kingdom"] <- "Eukaryota"
NW[which(NW$Target_Kingdom=="Euk"),"Target_Kingdom"] <- "Eukaryota"
NW[which((is.na(NW$Source_PhylumDivision)) & NW$Source_Kingdom=="Eukaryota"),"Source_PhylumDivision"] <- "unEuk"
NW[which((is.na(NW$Target_PhylumDivision)) & NW$Target_Kingdom=="Eukaryota"),"Target_PhylumDivision"] <- "unEuk"
NW[which(NW$Source_Kingdom=="Pro"),"Source_Kingdom"] <- "Prokaryota"
NW[which(NW$Target_Kingdom=="Pro"),"Target_Kingdom"] <- "Prokaryota"
NW[which((is.na(NW$Source_PhylumDivision)) & NW$Source_Kingdom=="Prokaryota"),"Source_PhylumDivision"] <- "unProk"
NW[which((is.na(NW$Target_PhylumDivision)) & NW$Target_Kingdom=="Prokaryota"),"Target_PhylumDivision"] <- "unProk"
NW[which(is.na(NW$Source_PhylumDivision)),]
NW[which(is.na(NW$Source_PhylumDivision)),]

# IDs
PhylumDivision_IDs <- unique(c(as.character(NW$Source_PhylumDivision), as.character(NW$Target_PhylumDivision)))
PhylumDivision_IDs <- c(sort(unique(c(NW$Source_PhylumDivision[which(substr(NW$Source,1,1)=="P" & NW$Source_Kingdom=="Archaea")],
                                           NW$Target_PhylumDivision[which(substr(NW$Target,1,1)=="P" & NW$Target_Kingdom=="Archaea")]))),
                             sort(unique(c(NW$Source_PhylumDivision[which(substr(NW$Source,1,1)=="P" & (NW$Source_Kingdom=="Bacteria" & NW$Source_PhylumDivision!="unBac"))],
                                           NW$Target_PhylumDivision[which(substr(NW$Target,1,1)=="P" & (NW$Target_Kingdom=="Bacteria" & NW$Target_PhylumDivision!="unBac"))]))),
                             sort(unique(c(NW$Source_PhylumDivision[which(substr(NW$Source,1,1)=="E" & NW$Source_PhylumDivision!="unEuk")],
                                           NW$Target_PhylumDivision[which(substr(NW$Target,1,1)=="E" & NW$Target_PhylumDivision!="unEuk")]))),
                             "unBac", "unEuk", "unProk")
PhylumDivision_IDs
my_grid_col <- data.frame(color= c(colorRampPalette(brewer.pal(5, "Reds")[-1])(4)[c(2,4,1,3)],
                                   c(colorRampPalette(brewer.pal(9,"YlGnBu")[-1])(13),colorRampPalette(brewer.pal(9,"YlGn")[-1])(12))[rev(c(1,25,2,24,3,23,4,22,5,21,6,20,7,19,8,18,9,17,10,16,11,15,12,14,13))],
                                   c(colorRampPalette(brewer.pal(9,"RdPu")[-1])(9),colorRampPalette(brewer.pal(9,"Purples")[-1])(9))[c(18,1,17,2,16,3,15,4,14,5,13,6,12,7,11,8,10,9)],
                                   "grey","grey","grey"))

rownames(my_grid_col) <- PhylumDivision_IDs
my_grid_col <- t(my_grid_col)

barplot(rep(10,50), col = my_grid_col)
t(my_grid_col)
```
3 <- grey
Arch <- 4
Bac <- 25
Euk <- 18
ARC                    color
Crenarchaeota       "#FB6A4A"
Euryarchaeota       "#A50F15"
Nanoarchaeaeota     "#FCAE91"
Thaumarchaeota      "#DE2D26"

BAC                    color
Acidobacteria       "#081D58"
Actinobacteria      "#F7FCB9"
Alphaproteobacteria "#182A7B"
Bacteroidetes       "#E3F4AB"
Calditrichaeota     "#243B97"
ChA                 "#CDEA9D"
ChO                 "#2253A3"
Cyanobacteria       "#B1DE8F"
Dadabacteria        "#206EB0"
Deinococcus-Thermus "#90D082"
Deltaproteobacteria "#1D8CBE"
Firmicutes          "#6DC173"
Gammaproteobacteria "#2EA3C2"
Gemmatimonadetes    "#4BAF62"
Hydrogenedentes     "#46B7C3"
Kiritimatiellaeota  "#339951"
Lentisphaerae       "#6AC5BE"
Margulisbacteria    "#1F8141"
NiN                 "#91D4B9"
NiR                 "#096F3A"
Planctomycetes      "#BBE4B5"
SAR406              "#005B31"
Schekmanbacteria    "#D6EFB2"
Spirochaetes        "#004529"
Verrucomicrobia     "#EDF8B1"

EUK                    color
Apicomplexa         "#3F007D"
Apusomonadidae      "#FDE0DD"
Centroheliozoa      "#51228C"
Cercozoa            "#FCC8C3"
Chlorophyta         "#64469D"
Choanoflagellida    "#FAA8B7"
Ciliophora          "#776CB1"
Cryptophyta         "#F87CA8"
Dinoflagellata      "#8F8BC1"
Fungi               "#EA4D9B"
Hilomonadea         "#A9A7CF"
Katablepharidophyta "#CB208D"
Mesomycetozoa       "#C3C4DF"
Ochrophyta          "#A0017C"
Picozoa             "#DCDCEC"
Radiolaria          "#730075"
Stramenopiles_X     "#EFEDF5"
Telonemia           "#49006A"

unBac               "grey"   
unEuk               "grey"   
unProk              "grey"

```{r}
PhylumDivision_IDs
```
 [1] "Crenarchaeota"       "Euryarchaeota"       "Nanoarchaeaeota"     "Thaumarchaeota"      "Acidobacteria"       "Actinobacteria"      "Alphaproteobacteria" "Bacteroidetes"       "Calditrichaeota"    
[10] "ChA"                 "ChO"                 "Cyanobacteria"       "Dadabacteria"        "Deinococcus-Thermus" "Deltaproteobacteria" "Firmicutes"          "Gammaproteobacteria" "Gemmatimonadetes"   
[19] "Hydrogenedentes"     "Kiritimatiellaeota"  "Lentisphaerae"       "Margulisbacteria"    "NiN"                 "NiR"                 "Planctomycetes"      "SAR406"              "Schekmanbacteria"   
[28] "Spirochaetes"        "Verrucomicrobia"     "Apicomplexa"         "Apusomonadidae"      "Centroheliozoa"      "Cercozoa"            "Chlorophyta"         "Choanoflagellida"    "Ciliophora"         
[37] "Cryptophyta"         "Dinoflagellata"      "Fungi"               "Hilomonadea"         "Katablepharidophyta" "Mesomycetozoa"       "Ochrophyta"          "Picozoa"             "Radiolaria"         
[46] "Stramenopiles_X"     "Telonemia"           "unBac"               "unEuk"               "noProk" 

### Save Taxa
```{r}
Nodes <- NW[,c("Source","Source_Kingdom","Source_PhylumDivision")]
colnames(Nodes) <- c("ID", "Kingdom", "PhylumDivision")
dt_temp <- NW[,c("Target","Target_Kingdom","Target_PhylumDivision")]
colnames(dt_temp) <- c("ID", "Kingdom", "PhylumDivision")
Nodes <- unique(rbind(Nodes, dt_temp))
v <- data.frame(ID = colnames(my_grid_col),
                color = my_grid_col["color",])
Nodes <- merge(Nodes,v,by.x="PhylumDivision",by.y="ID",all.x=TRUE,all.y=FALSE)

path <- paste(PATH, "00_Tables/", sep="")
filename <- "Nodes_Taxa.tsv"
write.table(Nodes, paste(path,filename,sep=""), col.names = TRUE, row.names = FALSE, sep = "\t", quote = TRUE)
```

### How many associations of a specific type?
```{r}
dt_temp <- NW[,c("Source_Kingdom","Target_Kingdom")]
table(dt_temp)
length(unique(c(as.character(NW$Source[which(NW$Source_Kingdom=="Archaea")]), as.character(as.character(NW$Source[which(NW$Source_Kingdom=="Archaea")])))))
length(unique(c(as.character(NW$Source[which(NW$Source_Kingdom=="Bacteria")]), as.character(as.character(NW$Source[which(NW$Source_Kingdom=="Bacteria")])))))
length(unique(c(as.character(NW$Source[which(NW$Source_Kingdom=="Eukaryota")]), as.character(as.character(NW$Source[which(NW$Source_Kingdom=="Eukaryota")])))))
length(unique(c(as.character(NW$Source[which(NW$Source_Kingdom=="Prokaryota")]), as.character(as.character(NW$Source[which(NW$Source_Kingdom=="Prokaryota")])))))
dt_temp <- NW[,c("Source_PhylumDivision","Target_PhylumDivision")]
#table(dt_temp)
```
              Target_Kingdom
Source_Kingdom Archaea Bacteria Eukaryota Prokaryota
    Archaea        818     1049         0          1
    Bacteria       722     7732         0         12
    Eukaryota      257     1888     16636          2
    Prokaryota       0        1         0          0
[1] 406
[1] 2009
[1] 2861
[1] 1

### Visualize
-> Circular Plot
-> most prevalent associations (>70%) per depth layer
```{r}
myorderSections <- PhylumDivision_IDs
mygridcolIDs <- PhylumDivision_IDs
path <- paste(PATH,"04_Prevalence/",sep="")
for(PERCENTAGE in c(0.7))
{
  print(paste("Percentage >", PERCENTAGE, "%"))
  dt_temp <-  merge(NW, PREV, by=c("Source","Target"))
  for(i in c("MS","NAO","SAO","SPO","NPO","IO"))
  {
    for(j in c("SRF","DCM","MES","BAT"))
    {
      # Circular Plot
      ## Initialize the layout
      #circos.initialize(factor=unique(N$Phylum), xlim=c(0,length(unique(N$Phylum))))
      myE <- dt_temp[which(dt_temp[,paste("Prevalence",i,j,sep="_")]>PERCENTAGE),c("Source_PhylumDivision", "Target_PhylumDivision",paste("Prevalence",i,j,sep="_"))]
      print(paste(i,j,dim(myE)[1]))
  
      if(dim(myE)[1]>0)
      {
        filename <- paste("PrevalenceAbove",PERCENTAGE*100,"percent_",i,"_",j,".pdf",sep="")
        pdf(file=paste(path,filename,sep=""), width = 3, height = 3)
        circos.par(gap.after = 5,   start.degree = 90, clock.wise = TRUE)

        # now, the image with rotated labels
        chordDiagram(myE, order = myorderSections, annotationTrack = "grid", preAllocateTracks = 2, col=my_grid_col["color",as.character(myE$Source_PhylumDivision)], grid.col = my_grid_col["color",mygridcolIDs])
        circos.trackPlotRegion(track.index = 2, panel.fun = function(x, y) {
            xlim = get.cell.meta.data("xlim")
            ylim = get.cell.meta.data("ylim")
            sector.name = get.cell.meta.data("sector.index")
            circos.text(mean(xlim), ylim[1] + .01, substr(sector.name,1,3), facing = "clockwise", niceFacing = TRUE, adj = c(-0.1, 0.5), cex = 0.5)
            #circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
        }, bg.border = NA)
  
        dev.off()
        # clear
        circos.clear()
      }
    }
  }
  
  myorderSections <- PhylumDivision_IDs
  mygridcolIDs <- PhylumDivision_IDs

  for(i in c("MS","NAO"))
  {
    for(j in c("EPI"))
    {
      # Circular Plot
      ## Initialize the layout
      #circos.initialize(factor=unique(N$Phylum), xlim=c(0,length(unique(N$Phylum))))
      myE <- dt_temp[which(dt_temp[,paste("Prevalence",i,j,sep="_")]>PERCENTAGE),c("Source_PhylumDivision", "Target_PhylumDivision",paste("Prevalence",i,j,sep="_"))]
      print(paste(i,j,dim(myE)[1]))
  
      if(dim(myE)[1]>0)
      {
        filename <- paste("PrevalenceAbove",PERCENTAGE*100,"percent_",i,"_",j,".pdf",sep="")
        pdf(file=paste(path,filename,sep=""), width = 3, height = 3)
        circos.par(gap.after = 5,   start.degree = 90, clock.wise = TRUE)

        # now, the image with rotated labels
        chordDiagram(myE, order = myorderSections, annotationTrack = "grid", preAllocateTracks = 2, col=my_grid_col["color",as.character(myE$Source_PhylumDivision)], grid.col = my_grid_col["color",mygridcolIDs])
        circos.trackPlotRegion(track.index = 2, panel.fun = function(x, y) {
            xlim = get.cell.meta.data("xlim")
            ylim = get.cell.meta.data("ylim")
            sector.name = get.cell.meta.data("sector.index")
            circos.text(mean(xlim), ylim[1] + .01, substr(sector.name,1,3), facing = "clockwise", niceFacing = TRUE, adj = c(-0.1, 0.5), cex = 0.5)
            #circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
        }, bg.border = NA)
  
        dev.off()
        # clear
        circos.clear()
      }
    }
  }
}
```
"Percentage > 0.7 %"
[1] "MS SRF 324"
[1] "MS EPI 307"
[1] "MS DCM 211"
[1] "MS MES 178"
[1] "MS BAT 338"

[1] "NAO SRF 297"
[1] "NAO EPI 1593"
[1] "NAO DCM 212"
[1] "NAO MES 147"
[1] "NAO BAT 38"

[1] "SAO SRF 133"
[1] "SAO DCM 1258"
[1] "SAO MES 143"
[1] "SAO BAT 120"

[1] "SPO SRF 459"
[1] "SPO DCM 1530"
[1] "SPO MES 399"
[1] "SPO BAT 217"

[1] "NPO SRF 493"
[1] "NPO DCM 557"
[1] "NPO MES 159"
[1] "NPO BAT 354"

[1] "IO SRF 336"
[1] "IO DCM 942"
[1] "IO MES 363"
[1] "IO BAT 123"

Check NAO: Malaspina vs Hotmix
```{r}
for(i in c("NAO"))
{
  for(j in c("SRF","EPI","DCM","MES","BAT"))
  {
    # Circular Plot
    ## Initialize the layout
    #circos.initialize(factor=unique(N$Phylum), xlim=c(0,length(unique(N$Phylum))))
    # Hotmix
    mydt_temp <- dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==i & SAM$layer==j)])]
    mydt_temp <- mydt_temp[,which(substr(colnames(mydt_temp),1,1)=="H")]
    prev_temp <- rowSums(mydt_temp)/dim(mydt_temp)[2]
    myE <- dt_temp[which(prev_temp>PERCENTAGE),c("Source_PhylumDivision", "Target_PhylumDivision",paste("Prevalence",i,j,sep="_"))]
    print(paste("Hotmix:",i,j,dim(myE)[1],dim(mydt_temp)[2]))
  
    if(dim(myE)[1]>0)
    {
      filename <- paste("Hotmix_PrevalenceAbove",PERCENTAGE*100,"percent_",i,"_",j,".pdf",sep="")
      pdf(file=paste(path,filename,sep=""), width = 3, height = 3)
      circos.par(gap.after = 5,   start.degree = 90, clock.wise = TRUE)

      # now, the image with rotated labels
      chordDiagram(myE, order = myorderSections, annotationTrack = "grid", preAllocateTracks = 2, col=my_grid_col["color",as.character(myE$Source_PhylumDivision)], grid.col = my_grid_col["color",mygridcolIDs])
      circos.trackPlotRegion(track.index = 2, panel.fun = function(x, y) {
          xlim = get.cell.meta.data("xlim")
          ylim = get.cell.meta.data("ylim")
          sector.name = get.cell.meta.data("sector.index")
          circos.text(mean(xlim), ylim[1] + .01, substr(sector.name,1,3), facing = "clockwise", niceFacing = TRUE, adj = c(-0.1, 0.5), cex = 0.5)
          #circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
      }, bg.border = NA)
  
      dev.off()
      # clear
      circos.clear()
    }
    
    # Malaspina
    mydt_temp <- dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==i & SAM$layer==j)])]
    mydt_temp <- mydt_temp[,which(substr(colnames(mydt_temp),1,1)=="M")]
    prev_temp <- rowSums(mydt_temp)/dim(mydt_temp)[2]
    myE <- dt_temp[which(prev_temp>PERCENTAGE),c("Source_PhylumDivision", "Target_PhylumDivision",paste("Prevalence",i,j,sep="_"))]
    print(paste("Malaspina:",i,j,dim(myE)[1],dim(mydt_temp)[2]))
  
    if(dim(myE)[1]>0)
    {
      filename <- paste("Malaspina_PrevalenceAbove",PERCENTAGE*100,"percent_",i,"_",j,".pdf",sep="")
      pdf(file=paste(path,filename,sep=""), width = 3, height = 3)
      circos.par(gap.after = 5,   start.degree = 90, clock.wise = TRUE)

      # now, the image with rotated labels
      chordDiagram(myE, order = myorderSections, annotationTrack = "grid", preAllocateTracks = 2, col=my_grid_col["color",as.character(myE$Source_PhylumDivision)], grid.col = my_grid_col["color",mygridcolIDs])
      circos.trackPlotRegion(track.index = 2, panel.fun = function(x, y) {
          xlim = get.cell.meta.data("xlim")
          ylim = get.cell.meta.data("ylim")
          sector.name = get.cell.meta.data("sector.index")
          circos.text(mean(xlim), ylim[1] + .01, substr(sector.name,1,3), facing = "clockwise", niceFacing = TRUE, adj = c(-0.1, 0.5), cex = 0.5)
          #circos.axis(h = "top", labels.cex = 0.5, major.tick.percentage = 0.2, sector.index = sector.name, track.index = 2)
      }, bg.border = NA)
  
      dev.off()
      # clear
      circos.clear()
    }
  }
}
```
NAO
[1] "NAO SRF 297 34"
[1] "NAO EPI 1593 4"
[1] "NAO DCM 212 6"
[1] "NAO MES 147 14"
[1] "NAO BAT 38 20"

Hotmix:
[1] "Hotmix: NAO SRF 1018 4"
[1] "Hotmix: NAO EPI 1593 4"
[1] "Hotmix: NAO DCM 845 4"
[1] "Hotmix: NAO MES 314 9"
[1] "Hotmix: NAO BAT 82 13"

Malaspina:
[1] "Malaspina: NAO SRF 427 30"
[1] "Malaspina: NAO EPI 0 0"
[1] "Malaspina: NAO DCM 32 2"
[1] "Malaspina: NAO MES 209 5"
[1] "Malaspina: NAO BAT 125 7"
