---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Vertical Connectivity
## Required Packages
```{r, echo=FALSE}
library(igraph)
library(ggplot2)
theme_set(theme_minimal())
library(dplyr)
library(RColorBrewer)
library(alluvial)
library(ggalluvial)
library(reshape)
```

## parameter and data
```{r}
PATH <- "GlobalNetworkMalaspinaHotmix/"

path <- paste(PATH,"00_Tables/",sep="")
filename <- "Sample_Classification.tsv"
SAM <- read.table(paste(path,filename,sep=""), header = TRUE)
filename <- "Nodes_Taxa.tsv"
TAX <- read.table(paste(path,filename,sep=""), header = TRUE)
rownames(TAX) <- TAX$ID
filename <- "ASV.txt"
Abund <- read.table(paste(path,filename,sep=""), header = TRUE)

path <- paste(PATH,"02_NetworkConstruction/",sep="")
filename <- "SampleSpecificSubnetworks.tsv"
NW <- read.table(paste(path,filename,sep=""), header = TRUE)

path <- paste(PATH,"04_Prevalence/",sep="")
filename <- "EdgePrevalence.tsv"
PREV <- read.table(paste(path,filename,sep=""), header = TRUE, stringsAsFactors = FALSE)
G <- graph_from_edgelist(as.matrix(PREV[,c("Source","Target")]))
vcount(G)
ecount(G)

path <- paste(PATH,"05_ClassifyingAssociations/",sep="")
filename <- "AssociationClassification_AbsentPresent.tsv"
dt_temp <- read.table(paste(path,filename,sep=""), header = TRUE)[,c("Source","Target","SRF","DCM","MES","BAT")]
```
5448 nodes and 29118 edges

# Associations present across all layers
- the following code generates a list of associations that appear in at least one region in each depth layer at least once
```{r}
dt_temp$Absent <- 0
regionIDs <- "MS_NAO_SAO_SPO_NPO_IO"
for(i in c("SRF","DCM","MES","BAT"))
{
  dt_temp$Absent[which(dt_temp[,i]=="Absent")] <- dt_temp$Absent[which(dt_temp[,i]=="Absent")] + 1
}
dt_temp <- dt_temp[which(dt_temp$Absent==0),]
dt_temp <- merge(dt_temp, PREV, by=c("Source","Target"), all.x=TRUE, all.y=FALSE)

dt_temp$AllLayers <- 0
for(j in c("MS","NAO","SAO","SPO","NPO","IO"))
{
  dt_temp[,paste(j,"allLayers",sep="_")] <- 0
  for(i in c("SRF","DCM","MES","BAT"))
  {
    dt_temp[which(dt_temp[,paste("Prevalence",j,i,sep="_")]>0),paste(j,"allLayers",sep="_")] <- dt_temp[which(dt_temp[,paste("Prevalence",j,i,sep="_")]>0),paste(j,"allLayers",sep="_")] + 1
  }
  dt_temp$AllLayers[which(dt_temp[,paste(j,"allLayers",sep="_")]==4)] <- dt_temp$AllLayers[which(dt_temp[,paste(j,"allLayers",sep="_")]==4)] + 1
}
dt_temp <- dt_temp[which(dt_temp$AllLayers>0),]
hist(dt_temp$AllLayers)
table(dt_temp$AllLayers)

dt_temp$Type <- paste(substr(dt_temp$Source,1,3), substr(dt_temp$Target,1,3), sep="_")
dt_temp$Type[which(dt_temp$Type=="Prok_Euk")] <- "Euk_Prok"
table(dt_temp$Type)

dt_temp <- merge(dt_temp, TAX[,c("ID","PhylumDivision")], by.x="Source", by.y="ID", all.x=TRUE, all.y=FALSE)
colnames(dt_temp)[which(colnames(dt_temp)=="PhylumDivision")] <- "Source_PhylumDivision"
dt_temp <- merge(dt_temp, TAX[,c("ID","PhylumDivision")], by.x="Target", by.y="ID", all.x=TRUE, all.y=FALSE)
colnames(dt_temp)[which(colnames(dt_temp)=="PhylumDivision")] <- "Target_PhylumDivision"
taxa <- as.data.frame(table(dt_temp[,c("Source_PhylumDivision","Target_PhylumDivision")]))
taxa <- taxa[which(taxa$Freq>0),]

path <- paste(PATH,"06_VerticalConnectivity/",sep="")
filename <- "AllLayersAssociations.txt" 
write.table(dt_temp, paste(path,filename,sep=""),col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t")
```
Euk_Euk Euk_Pro Pro_Pro 
    119      13     327 

# Vertical connectivity of associations
## generating table
- colums = regions (MS, NAO, SAO, SPO, NPO, IO)
- rows = taxa (Arch, Bac, Euk + AA, AB, AE, BB, BE, EE)
```{r}
dt_Vis <- data.frame(Source=character(),
                      Target=character(),
                      ID=character(),
                      Box=character(),
                      FirstDetected=character(),
                      Region=character(),
                      Layer=character(),
                      stringsAsFactors = FALSE)

dt_template <- data.frame(Source=as.character(NW$Source),
                          Target=as.character(NW$Target),
                          ID=paste(substr(as.character(TAX$Kingdom[NW$Source]),1,3), substr(as.character(TAX$Kingdom[NW$Target]),1,3), sep="_"),
                          Box=rep("A",dim(NW)[1]),
                          FirstDetected=NA,
                          #Region=rep(REGION,dim(NW)[1]),
                          #Layer=rep("to add",dim(NW)[1]),
                          stringsAsFactors = FALSE)
dt_template$ID[which(dt_template$ID=="Bac_Arc")] <- "Arc_Bac"
dt_template$ID[which(dt_template$ID=="Euk_Arc")] <- "Arc_Euk"
dt_template$ID[which(dt_template$ID=="Euk_Bac")] <- "Bac_Euk"
    
for(REGION in c("MS","NAO","SAO","NPO","IO"))
{
    # Surface
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "SRF"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "S"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # DCM
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "DCM"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0)] <- "D"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0)] <- "DCM"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # Mesopelagic
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "MES"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "D"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "M"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0)] <- "DCM"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "MES"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # Bathypelagic
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "BAT"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "D"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "M"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "B"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))>0)] <- "DCM"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "MES"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "BAT"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
}

REGION <- "SPO"
    # Surface
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "SRF"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "S"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # DCM
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "DCM"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0)] <- "D"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0)] <- "DCM"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # Mesopelagic
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "MES"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "D"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "M"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0)] <- "DCM"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "MES"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
    
    # Bathypelagic
    dt_temp <- dt_template
    dt_temp$Region <- REGION
    dt_temp$Layer <- "BAT"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "S"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "D"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "M"
    dt_temp$Box[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                              1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))==0 &
                      rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "B"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))>0)] <- "SRF"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)>0)] <- "DCM"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))>0)] <- "MES"
    dt_temp$FirstDetected[which(rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])]>0))==0 &
                                        1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])]>0))==0 &
                                rowSums(1*(NW[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])]>0))>0)] <- "BAT"
    dt_Vis <- rbind(dt_Vis, dt_temp[which(!is.na(dt_temp$FirstDetected)),])
```

## Visualization
```{r}
mycolor_id <- c(SRF="yellow",
                DCM="orange",
                MES="red",
                BAT="black",
                S="yellow",
                D="orange",
                M="red",
                B="black",
                A="white")

dt_Vis$edge <- paste(dt_Vis$Source, dt_Vis$Target, sep=";")
dt_Vis$Freq <- 1
head(dt_Vis)

p <- ggplot(data = dt_Vis,
            aes(x = factor(Layer, levels=c("BAT","MES","DCM","SRF")), stratum = factor(Box, levels=rev(c("S","D","M","B","A"))), alluvium = edge,
                y = Freq, label = Box)) +
            geom_alluvium(aes(color=FirstDetected), alpha=0.6) +
            geom_stratum(aes(fill=Box), width = 0.35, alpha = 0.6) +
            scale_fill_manual(values=mycolor_id) +
            scale_color_manual(values=mycolor_id) +
            #geom_text(stat = "stratum") +
            xlab("Depth layer") + ylab("Frequency") +
            theme_classic() +
            theme(text = element_text(size=10), legend.position = "bottom", legend.title = element_blank(),
                  axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_line(color="black"),
                  axis.title.y = element_text(color="black"), axis.title.x = element_text(color="black")) +
            coord_flip() +
            facet_grid(factor(Region, levels=c("MS","NAO","SAO","SPO","NPO","IO"))~ID, scales = "free")
path <- paste(PATH,"06_VerticalConnectivity/",sep="")
filename <- paste(path,"AlluvialPlot.png")
ggsave(filename, plot = p, height = 8, width = 15)

# How many are new?
for(i in unique(dt_Vis$Region))
{
  for(j in unique(dt_Vis$Layer))
  {
    print(paste(i,j,sep="_"))
    print(table(dt_Vis$Box[which(dt_Vis$Region==i & dt_Vis$Layer==j)]))
    print(table(dt_Vis$Box[which(dt_Vis$Region==i & dt_Vis$Layer==j)])/length(which(dt_Vis$Region==i & dt_Vis$Layer==j & dt_Vis$Box!="A"))*100)
  }
}
```

# Vertical connectivity of ASVs
## generating table
Same as above but ASVs
```{r}
REGIONids <- c("MS","NAO","SAO","SPO","NPO","IO")
DEPTHids <- c("SRF","DCM","MES","BAT")
path <- paste(PATH,"06_VerticalConnectivity/",sep="")
for(REGION in REGIONids){
  RLids <- c(paste(REGION, DEPTHids, sep = "_"))
  dt_temp <- Abund[,c("ID",as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer!="EPI")]))]
  dt_temp <- dt_temp[which(rowSums(1*(dt_temp[,-1]>0))>0),]
  dt_alluvial <- data.frame(ID=dt_temp[,c("ID")])
  dt_alluvial$SRF <- "absent"
  dt_alluvial$SRF[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0)] <- "SRF"
  
  dt_alluvial$DCM <- "absent"
  if(length(which(SAM$OceanRegion==REGION & SAM$layer=="DCM"))>1){
      dt_alluvial$DCM[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                        rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])>0)] <- "SRF"
      dt_alluvial$DCM[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                        rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])>0)] <- "DCM"
  }else{
      dt_alluvial$DCM[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)] <- "SRF"
      dt_alluvial$DCM[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0)] <- "DCM"
  }
  
  dt_alluvial$MES <- "absent"
  if(length(which(SAM$OceanRegion==REGION & SAM$layer=="DCM"))>1){
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "SRF"
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "DCM"
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "MES"
  }else{
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "SRF"
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "DCM"
      dt_alluvial$MES[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0)] <- "MES"
  }
  
  dt_alluvial$BAT <- "absent"
  if(length(which(SAM$OceanRegion==REGION & SAM$layer=="DCM"))>1){
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "SRF"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "DCM"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "MES"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])])==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "BAT"
  }else{
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])>0 &
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "SRF"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "DCM"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])>0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "MES"
      dt_alluvial$BAT[which(rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="SRF")])])==0 &
                                    dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="DCM")])]==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="MES")])])==0 & 
                            rowSums(dt_temp[,as.character(SAM$Sample[which(SAM$OceanRegion==REGION & SAM$layer=="BAT")])])>0)] <- "BAT"
  }

  dt_alluvial$Freq <- 1
  dt_aggregate <- aggregate( Freq ~ SRF + DCM + MES + BAT, data=dt_alluvial, sum)
  
  alluvial(dt_aggregate[,1:4], freq=dt_aggregate$Freq, border=NA, cex=1,
           blocks = TRUE,
           col=ifelse((substr(dt_aggregate$SRF,1,3) == "SRF"), "yellow", 
                      ifelse((substr(dt_aggregate$SRF,1,3) == "abs" & substr(dt_aggregate$DCM,1,3) == "DCM"), "orange",
                             ifelse((substr(dt_aggregate$SRF,1,3) == "abs" & substr(dt_aggregate$DCM,1,3) == "abs" & (substr(dt_aggregate$MES,1,3) == "MES")), "red",
                                    ifelse((substr(dt_aggregate$SRF,1,3) == "abs" & substr(dt_aggregate$DCM,1,3) == "abs" & substr(dt_aggregate$MES,1,3) == "abs" & substr(dt_aggregate$BAT,1,3) == "BAT"), "black", "gray")))))
  
  idorder <- c("absent", rev(DEPTHids))
  dt_aggregate$layerID <- "absent"
  dt_aggregate$layerID[which(dt_aggregate$SRF=="SRF")] <- "SRF"
  dt_aggregate$layerID[which(dt_aggregate$SRF=="absent" & dt_aggregate$DCM=="DCM")] <- "DCM"
  dt_aggregate$layerID[which(dt_aggregate$SRF=="absent" & dt_aggregate$DCM=="absent" & dt_aggregate$MES=="MES")] <- "MES"
  dt_aggregate$layerID[which(dt_aggregate$SRF=="absent" & dt_aggregate$DCM=="absent" & dt_aggregate$MES=="absent" & dt_aggregate$BAT=="BAT")] <- "BAT"
  mycolor_id <- c(SRF="yellow",
                DCM="orange",
                MES="red",
                BAT="black",
                absent="light grey")

  p <- ggplot(data = dt_aggregate,aes(axis1 = factor(BAT, levels = c("absent",rev(DEPTHids))),
                                    axis2 = factor(MES, levels = c("absent",rev(DEPTHids))),
                                    axis3 = factor(DCM, levels = c("absent",rev(DEPTHids))),
                                    axis4 = factor(SRF, levels = c("absent",rev(DEPTHids))),
                                    y = Freq)) +
  scale_x_discrete(limits = rev(c("SRF", "DCM",  "MES", "BAT")), expand = c(0, 0)) +
  xlab("") + ylab(REGION) +
  geom_alluvium(aes(fill = factor(layerID, levels=idorder))) +
  geom_stratum(width=0.1, color="black") +
  geom_text(stat = "stratum", aes(label = substr(after_stat(stratum),1,1))) +
  theme_classic() + theme(text = element_text(size=12), legend.position = "none",
                          axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.ticks.x = element_line(color="black"),
                          axis.title.y = element_text(color="black"), axis.title.x = element_text(color="black")) +
  scale_fill_manual(values=mycolor_id) +
  coord_flip()

  filename <- paste(path,"Alluvial_ASV_", REGION,".pdf",sep="")
  ggsave(filename, plot = p, width = 5, height = 5)
}
```