---
title: "Global Ocean"
author: "Ina Maria Deutschmann"
date: "15. July 2021"
---

# Network Similarity
## Required Packages
```{r, echo=FALSE}
library(igraph)
library(ggplot2)
require(reshape2)
library(ape)
theme_set(theme_minimal())
```

## parameter and data
```{r}
PATH <- "GlobalNetworkMalaspinaHotmix/"

path <- paste(PATH,"00_Tables/",sep="")
filename <- "Sample_Classification.tsv"
SAM <- read.table(paste(path,filename,sep=""), header = TRUE)

path <- paste(PATH,"02_NetworkConstruction/",sep="")
filename <- "SampleSpecificSubnetworks.tsv"
NW <- read.table(paste(path,filename,sep=""), header = TRUE)
```
5448 nodes and 29118 edges

## Shared edges
Repeatability score as average pairwise edge overlap between two networks (Jaccard similarity coefficient between two sets of network edges)
We calculate a repeatability score as the size of the set of intersection of network edges divided by the size of the set of the union of the networks edges between two networks.

# Average of all pairwise Jaccard indices
Given 12 years, the average Jaccard index is the mean of all Jaccard indices of pairwise network comparisons
```{r}
N <- NW[,grep("m",colnames(NW))]
N_Intersection <- as.matrix(t(N))%*%as.matrix(N)
N_Union <- matrix(data = 0, nrow = dim(N_Intersection)[1], ncol = dim(N_Intersection)[2])
for(i in 1:(dim(N)[2]-1))
{
  for(j in (i+1):dim(N)[2])
  {
    N_Union[i,j] <- length(which(N[,i]>0 | N[,j]>0))
  }
}
N_RepeatabilityScore <- N_Intersection / N_Union
RepeatabilityScores <- as.vector(N_RepeatabilityScore)
RepeatabilityScores <- RepeatabilityScores[which(RepeatabilityScores<1)]
average_RepeatabilityScore <- sum(RepeatabilityScores) / length(RepeatabilityScores)
paste(sum(RepeatabilityScores), " / ", length(RepeatabilityScores), " = ", sum(RepeatabilityScores) / length(RepeatabilityScores), sep ="")
```
Average (mean): 4399.08760475968 / 78606 = 0.0559637636409393"

Save
```{r}
v_temp <- data.frame(Source=NA, Target=NA, J=N_RepeatabilityScore[upper.tri(N_RepeatabilityScore)], stringsAsFactors = FALSE)
c_temp <- 1
for(i in c(2:dim(N_RepeatabilityScore)[1])){
  for(j in c(1:(i-1))){
    v_temp[c_temp, "Source"] <- colnames(N_RepeatabilityScore)[i]
    v_temp[c_temp, "Target"] <- rownames(N_RepeatabilityScore)[j]
    c_temp <- c_temp + 1
  }
}
path <- paste(PATH,"07_NetworkSimilarity/SharedEdges/",sep="")
filename <- "nw_comparison_EdgeSet_edgelist.tsv"
write.table(v_temp, paste(path,filename,sep=""), row.names = FALSE, col.names = TRUE, quote = FALSE, dec = ".", sep = "\t")
```

Stats
```{r}
summary(v_temp$J)
```
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.000000 0.002894 0.015107 0.055964 0.065418 0.766038 

## Violin and Boxplot
```{r}
dodge <- position_dodge(width = 0.9)
p_J_all <- ggplot(v_temp, aes(x="all", y=J)) + xlab("Jaccard index") + ylab("") +
                      geom_violin(position = dodge) + #geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + 
                      geom_boxplot(width=0.05,position=dodge, alpha = 0.8, color = "grey") +
                      theme(text = element_text(size=20))
p_J_all
```

# 2_Graphlet
https://www.nature.com/articles/srep04547
http://www0.cs.ucl.ac.uk/staff/natasa/GCD/index.html
1. Transform networks into Leda (.gw) format (here in R)
2. Compute the graphlet degree vector signatures of each network using the provided script: "python count.py my_network.gw"
3. Compute GCD-11, (all networks and their signature files must be in the same folder):  "python network_folder gcd11 n", where n=#threads

## 1. Save each subnetwork in Leda format
```{r}
N <- NW[,c(1,2,grep("m",colnames(NW)))]
path <- paste(PATH,"07_NetworkSimilarity/Graphlet/Subnetworks/",sep="")
for(i in colnames(N)[-c(1,2)])
{
  G <- graph_from_edgelist(as.matrix(N[which(N[,i]>0),c("Source","Target")]))

  filename <- paste(path,i,".gw",sep="")
  write_graph(G, filename, format = c("leda"))
}
```

## 2. Compute graphlet degree vector signatures
- change path if needed!
```{bash}
cd GlobalNetworkMalaspinaHotmix/07_NetworkSimilarity/Graphlet/Subnetworks
echo "# Compute graphlet degree vector signatures\n" > Log.txt
for f in *.gw;
do
  echo "# Processing $f" >> Log.txt
  python ../count/count.py $f >> Log.txt
done
cd ..
```

## 3. Compute GCD-11, (all networks and their signature files must be in the same folder):  "python network_folder gcd11 n", where n=#threads
- I used adjusted the program from: http://www0.cs.ucl.ac.uk/staff/natasa/GCD/index.html
          Supplementary Information for: "Revealing the Hidden Language of Complex Networks"
          O. N. Yaveroglu, N. Malod-Dognin, D. Davis, Z. Levnajic, V. Janjic, R. Karapandza, A. Stojmirovic, and N. Przulj
- see: "Adjustments_to_original_code.txt" in the folder "Graphlet"    
- change path if needed!
```{bash}
# All -> too big, doesn't work on Laptop (at least not in reasonable time)
cd GlobalNetworkMalaspinaHotmix/07_NetworkSimilarity/Graphlet
echo "# Compute GCD-11\n" > Log_all.txt
mkdir temp

echo "# all\n"  >> Log_all.txt
cp Subnetworks/* temp/
python networkComparison.py temp/ gcd11 1 >> Log_all.txt
cp temp/gcd11.txt ./gcd11_all.txt
rm temp/gcd11.txt
rm -r temp

# Partially
cd GlobalNetworkMalaspinaHotmix/07_NetworkSimilarity/Graphlet
echo "# Compute GCD-11\n" > Log_partial.txt
mkdir tempP

echo "# Hotmix\n"  >> Log_partial.txt
cp Subnetworks/Hotmix* tempP/
python networkComparison.py tempP/ gcd11 1 >> Log_partial.txt
cp tempP/gcd11.txt ./gcd11_Hotmix.txt
rm tempP/gcd11.txt

echo "# Hotmix and MalaSurf\n"  >> Log_partial.txt
cp Subnetworks/MalaSurf* tempP/
python networkComparison.py tempP/ gcd11 1 >> Log_partial.txt
cp tempP/gcd11.txt ./gcd11_Hotmix_MalaSurf.txt
rm tempP/gcd11.txt
rm tempP/MalaSurf*

echo "# Hotmix, MalaDeep, and MalaVP\n"  >> Log_partial.txt
cp Subnetworks/MalaDeep* tempP/
cp Subnetworks/MalaVP* tempP/
python networkComparison.py tempP/ gcd11 1 >> Log_partial.txt
cp tempP/gcd11.txt ./gcd11_Hotmix_MalaDeep_MalaVP.txt
rm tempP/Hotmix*

echo "# MalaSurf, MalaDeep, and MalaVP\n"  >> Log_partial.txt
cp Subnetworks/MalaSurf* tempP/
python networkComparison.py tempP/ gcd11 1 >> Log_partial.txt
cp tempP/gcd11.txt ./gcd11_MalaSurf_MalaDeep_MalaVP.txt
rm -r tempP
```

## 4. Upload matrix
Combine
```{r}
path <- paste(PATH,"02_NetworkConstruction/",sep="")
filename <- "SampleSpecificSubnetworks.tsv"
NW <- read.table(paste(path,filename,sep=""), header = TRUE)
stationIDs <- colnames(NW)[grep("_",colnames(NW))]
nw_comp_graphlet <- matrix(nrow=length(stationIDs), ncol=length(stationIDs))
colnames(nw_comp_graphlet) <- stationIDs
rownames(nw_comp_graphlet) <- stationIDs

# Hotmix
path <- paste(PATH,"07_NetworkSimilarity/Graphlet/",sep="")
filename <- "gcd11_Hotmix.txt"
dt_temp <- read.table(paste(path,filename,sep=""), header = TRUE)
colnames(dt_temp) <- gsub("tempP.", "", colnames(dt_temp))
rownames(dt_temp) <- gsub("tempP/", "", rownames(dt_temp))

dt_temp <- as.matrix(dt_temp)
nw_comp_graphlet[rownames(dt_temp),colnames(dt_temp)] <- dt_temp

# Hotmix and MalaSurf
filename <- "gcd11_Hotmix_MalaSurf.txt"
dt_temp <- read.table(paste(path,filename,sep=""), header = TRUE)
colnames(dt_temp) <- gsub("tempP.", "", colnames(dt_temp))
rownames(dt_temp) <- gsub("tempP/", "", rownames(dt_temp))

dt_temp <- as.matrix(dt_temp)
nw_comp_graphlet[rownames(dt_temp),colnames(dt_temp)] <- dt_temp

# Hotmix, MalaDeep, and MalaVP
filename <- "gcd11_Hotmix_MalaDeep_MalaVP.txt"
dt_temp <- read.table(paste(path,filename,sep=""), header = TRUE)
colnames(dt_temp) <- gsub("tempP.", "", colnames(dt_temp))
rownames(dt_temp) <- gsub("tempP/", "", rownames(dt_temp))

dt_temp <- as.matrix(dt_temp)
nw_comp_graphlet[rownames(dt_temp),colnames(dt_temp)] <- dt_temp

# MalaSurf, MalaDeep, and MalaVP
filename <- "gcd11_MalaSurf_MalaDeep_MalaVP.txt"
dt_temp <- read.table(paste(path,filename,sep=""), header = TRUE)
colnames(dt_temp) <- gsub("tempP.", "", colnames(dt_temp))
rownames(dt_temp) <- gsub("tempP/", "", rownames(dt_temp))

dt_temp <- as.matrix(dt_temp)
nw_comp_graphlet[rownames(dt_temp),colnames(dt_temp)] <- dt_temp

# NAs?
which(is.na(nw_comp_graphlet))

# Save
filename <- "nw_comparison_graphlet_matrix.txt"
write.table(nw_comp_graphlet, paste(path,filename,sep=""), row.names = TRUE, col.names = TRUE, quote = FALSE, dec = ".", sep = "\t")
```

```{r}
isSymmetric(nw_comp_graphlet) # TRUE
nw_comp_graphlet[lower.tri(nw_comp_graphlet)] <- NA
diag(nw_comp_graphlet) <- NA
E <- melt(nw_comp_graphlet)
E <- E[which(!is.na(E$value)),]
colnames(E) <- c("Source","Target","gdc_11")

## Save
filename <- "nw_comparison_graphlet_edgelist.tsv"
write.table(E, paste(path,filename,sep=""), row.names = FALSE, col.names = TRUE, quote = FALSE, dec = ".", sep = "\t")
```

## Visualization of graphlet
Boxplot all
```{r}
dodge <- position_dodge(width = 0.9)
p_g_all <- ggplot(E, aes(x="all", y=gdc_11)) + xlab("gdc_11") + ylab("") + ylim(c(0,1.8)) +
                      geom_violin(position = dodge) + #geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + 
                      geom_boxplot(width=0.1,position=dodge, alpha = 0.8, color = "grey") +
                      theme(text = element_text(size=20))
p_g_all
```

# Minimal Spanning Tree
```{r}
# Determine MST
path <-  paste(PATH,"07_NetworkSimilarity/Graphlet/",sep="")
filename <- "nw_comparison_graphlet_matrix.txt"
nwsim <- read.table(paste(path,filename,sep=""),header=TRUE)
myMST <- mst(as.dist(nwsim))
dim(myMST)
rownames(myMST)==colnames(myMST)
isSymmetric.matrix(as.matrix(myMST))

# Convert adjacency matrix to edgelist
G <- graph.adjacency(as.matrix(myMST), mode = "undirected")
Edgelist <- as.data.frame(get.edgelist(G))
colnames(Edgelist) <- c("Source","Target")
head(Edgelist)

# Save
path <-  paste(PATH,"07_NetworkSimilarity/MST/",sep="")
filename <- "MST.tsv"
write.table(Edgelist, paste(path,filename,sep=""), col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE)
```
